Characterizing subarctic European vegetation for land surface modeling of ozone pollution and climate risk

### 2021-09-27 VegOzone.tex
Placing of appendix figure
Rearange text

Initial test simulations with the MM PFTs revealed an unrealistically low stomatal conductance at leaf-level ($G_\mathrm{sto}^\mathrm{leaf}$) in 2019 particularly for perennial grassland (Appendix~Fig.~\ref{fig:pody_mm_composit}). Substantial stomatal conductance occured only during an extended warm period in late July. In ecological terms, this means that there was almost no growth of grass in the summer of 2019 -- a prediction which is easily falsified by reality. We identified $f_\mathrm{T}$ as abnormally low, being the limiting factor of stomatal conductance in perennial grassland. Therefore, we saw the necessity to propose bespoke parameterizations describing an acclimation of of the PFTs to the climatic conditions in the target region. Note, however, that these parameterizations are hypothetical and have yet to be verified by experiments.

We assume that perennial vegetation will likely maximize carbon acquisition during the short subarctic growing season. Because the mapping manual version of the $\mathrm{DO_3SE}$ model currently does not simulate net photosynthesis ($A_\mathrm{n}$), we assume a first order proportionality between $A_\mathrm{n}$ and $g_\mathrm{sto}$ \citep{GCB:Medlyn2011} and effectively tune the temperature and light response functions ($f_\mathrm{T}$ and $f_\mathrm{light}$) for higher $\left<g_\mathrm{sto}\right>/g_\mathrm{max}$ (see Appendix~\ref{appendix:do3se_model} for details) to acclimate the growth potential to the local climate. We further assume that $f_\mathrm{VPD}$ and $f_\mathrm{SWP}$ suit our biomes. The procedure is graphically illustrated in Fig.~\ref{fig:f_temp_grassland} for grassland. We aim to increase the overlapping area between the probability density function (PDF) and the respective response function. We show two climatological reference periods 1990s and 2000s to indicate that the vegetation is subject to ongoing climate change and hence continuous acclimation. The resulting response functions for coniferous and deciduous trees are displayed in Appendix~Figs.~\ref{fig:f_temp_spruce}--\ref{fig:f_temp_birch}, respectively.

We define two different hypothetical temperature acclimations: \emph{subarctic} and \emph{cold}. For either, we assume that the hypothetical species are more tolerant to cold conditions and shift $f_\mathrm{T}$ towards colder temperatures accordingly. We construct \emph{cold} as representative for a species that is more tolerant to cold temperatures, but slightly less efficient at warm temperatures compared to MM. In the same way, \emph{subarctic} refers to a hypothetical species which is very tolerant to cold but is sensitive to high temperatures, and most efficient at cool temperatures ($T_\mathrm{opt}$ close to the climatological mean temperature of 1992--2000). The most extreme of the two acclimation types is \emph{subarctic}. For perennial grassland the resulting response functions are depicted together with a five month growing season temperature PDF of the two periods 1992-2000 and 2011-2019 in Fig.~\ref{fig:f_temp_grassland}a).

@@

\appendix
\section{Growing season}
\label{appendix:growing_season}
\begin{figure*}[t]
  \includegraphics[width=12cm]{greening_season_change_Svanvik}
  \caption{Estimated shift and prolongation of growing season at Svanhovd over the past 6 decades based on data from \citet{SeNorge}.}
  \label{fig:greening_season_change_Svanvik}
\end{figure*}

>>>>

Initial test simulations with the MM PFTs revealed an unrealistically low stomatal conductance at leaf-level ($G_\mathrm{sto}^\mathrm{leaf}$) in 2019 particularly for perennial grassland (Appendix~Fig.~\ref{fig:pody_mm_composit}). Substantial stomatal conductance occurred only during an extended warm period in late July. In ecological terms, this means that there was almost no growth of grass in the summer of 2019 -- a prediction which is easily falsified by reality. We identified $f_\mathrm{T}$ as abnormally low, being the limiting factor of stomatal conductance in perennial grassland. Therefore, we saw the necessity to propose bespoke parameterizations describing an acclimation of of the PFTs to the climatic conditions in the target region. Note, however, that these parameterizations are hypothetical and have yet to be verified by experiments.

We assume that perennial vegetation will likely maximize carbon acquisition during the short subarctic growing season. Because the mapping manual version of the $\mathrm{DO_3SE}$ model currently does not simulate net photosynthesis ($A_\mathrm{n}$), we assume a first order proportionality between $A_\mathrm{n}$ and $g_\mathrm{sto}$ \citep{GCB:Medlyn2011} and effectively tune the temperature and light response functions ($f_\mathrm{T}$ and $f_\mathrm{light}$) for higher $\left<g_\mathrm{sto}\right>/g_\mathrm{max}$ (see Appendix~\ref{appendix:do3se_model} for details) to acclimate the growth potential to the local climate. We further assume that $f_\mathrm{VPD}$ and $f_\mathrm{SWP}$ suit our vegetation types. We aim to increase the overlapping area between the probability density function (PDF) and the respective response function.

We define two different hypothetical temperature acclimations: \emph{subarctic} and \emph{cold}. For either, we assume that the hypothetical species are more tolerant to cold conditions and shift $f_\mathrm{T}$ towards colder temperatures accordingly. We construct \emph{cold} as representative for a species that is more tolerant to cold temperatures, but slightly less efficient at warm temperatures compared to MM. In the same way, \emph{subarctic} refers to a hypothetical species which is very tolerant to cold but is sensitive to high temperatures, and most efficient at cool temperatures ($T_\mathrm{opt}$ close to the climatological mean temperature of 1992--2000).
We show two climatological reference periods 1990s and 2000s to indicate that the vegetation is subject to ongoing climate change and hence continuous acclimation. The most extreme of the two acclimation types is \emph{subarctic}. For perennial grassland the resulting response functions are depicted together with a five month growing season temperature PDF of the two periods 1992-2000 and 2011-2019 in Fig.~\ref{fig:f_temp_grassland}a.

The resulting response functions for coniferous and deciduous trees are displayed in Appendix~Figs.~\ref{fig:f_temp_spruce} and \ref{fig:f_temp_birch}, respectively.

@@

\appendix
\section{Growing season}
\label{appendix:growing_season}

\begin{figure*}[th]
  \includegraphics[width=12cm]{greening_season_change_Svanvik}
  \caption{Estimated shift and prolongation of growing season at Svanhovd over the past 6 decades based on data from \citet{SeNorge}.}
  \label{fig:greening_season_change_Svanvik}
\end{figure*}
